---
title: "spatialHeatmap Shiny App"
author: ""
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output:
  BiocStyle::html_document:
    css: landing.css
    toc: false
    toc_float:
        collapsed: true
        smooth_scroll: true
    toc_depth: 4
    fig_caption: yes
    code_folding: hide
    number_sections: true
    self_contained: true
fontsize: 14pt
bibliography: bibtex.bib
---

```{css, echo=FALSE}
pre code {
white-space: pre !important;
overflow-x: scroll !important;
word-break: keep-all !important;
word-wrap: initial !important;
}
```

```{r global_options, include=FALSE}
## ThG: chunk added to enable global knitr options. The below turns on
## caching for faster vignette re-build during text editing.
#knitr::opts_chunk$set(cache=TRUE)
```
<!-- 

<style type="text/css">
 .main-container { max-width: 1800px; margin-left: 5px; margin-right: auto; }
</style>

<style>body { text-align: justify }</style>  


```{r css, echo = FALSE, results = 'asis'}
BiocStyle::markdown(css.files=c('file/custom.css'))
```

-->

```{r setup0, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr); opts_chunk$set(message=FALSE, warning=FALSE)
```

The spatialHeatmap Shiny App is the graphical implementation of most functionalities in the [spatialHeatmap](https://bioconductor.org/packages/devel/bioc/html/spatialHeatmap.html){target="_blank"} software, which is specialized in visualizing spatial bulk and single cell assays in anatomical images.

The functional modules in this App includes spatial heatmap, spatial enrichment, large-scale data mining, and co-visualization. Compared with command-line usage in R, the Shiny App includes a variety of convenience features that will appeal to experimentalists and users less familiar with R, such as selecting genes by clicking rows in interactive tables, customizing color schemes, full-screen display, downloading images, and providing pre-uploaded data sets for testing or demonstration purposes. The Shiny App can be used on both local computers as well as centralized server-based deployments (e.g., cloud-based or custom servers) to support both private or shared analyses.  


